\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Motivation Letter Praktikum KI}
\author{Niklas Weber, Steven Mkhitarian, Oussama Bourhalem}
\date{May 2025}

\begin{document}
\maketitle

% \title{Introduction}
Dear JaxAtari Lab Team,

We are a group of three Master’s students in Information Systems at TU Darmstadt, driven by an enthusiasm for practical applications of AI and a profound interest in reinforcement learning. Over the course of our studies, we have developed a strong background in the construction and extension of AI-based game environments, and we are eager to bring our experience and creativity to your Practical Lab in AI.

Our motivation to contribute to the lab comes from our hands-on expertise with game modification. In particular, we have identified several innovative enhancements for the skiing environment. We propose to refine the visual and logical aspects of the game by extending the player’s avatar. With our planned modifications, when the player steers left or right, the skier will dynamically lean in the corresponding direction, thereby adding a layer of realism to the interaction. In addition, the gameplay will be enriched by allowing the player to jump over obstacles, while the in-game timer will now continue past 254. To ensure a robust gaming experience, we have also implemented a mechanism that resets the game whenever the skier collides with an obstacle while moving downhill.

We have already set up and executed the JaxAtari environment on our local machines and have gained an understanding of its structure. Building on this groundwork, our initial work involves dynamically linking the steering logic with directional sprites to realize the skier’s lean effect. Our collaborative skill set, which spans programming in both JAX and Pygame, positions us well to contribute meaningful improvements to the platform.

We are genuinely excited about the prospect of contributing to a modern, collaborative, and open-source reinforcement learning project. Our commitment is to deliver clean, efficient, and well-documented code that not only adds value to the game’s mechanics but also paves the way for further research and user studies.

Thank you for considering our proposal. We would be glad to join the lab and help drive this project forward with innovative enhancements and diligent work.

Kind regards, 

Niklas Weber, Steven Mkhitarian, Oussama Bourhalem 

\end{document}
